Solution of near-Toeplitz tridiagonal systems on GPU-accelerated clusters

### 2016-03-16 paper-draft/paper.tex
changes due to Dr. Livescu

\usepackage{amsmath,bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{rotating}

@@

Thus, in the best case ($n$ parallel processors),
cyclic reduction requires 
$2log_2(n) - 1$ steps.
For even moderately large $n$,
this is significantly smaller than
the $2n$ steps required by the classical Thomas algorithm.
This makes cyclic reduction a good fit
for massively parallel architectures like GPUs.

@@

\begin{align}
& \begin{bmatrix}
b_1^p & c_1^p \\
a_2^p & b_2^p & c_2^p \\
      & a_3^p & b_3^p & c_3^p \\
      &       & a_4^p & b_4^p & c_4^p \\
      &       &       &       &  \ddots & c_{m-1}^p\\
      &       &       &       &     a_{m}^p  & b_{m}^p
\end{bmatrix}
\begin{bmatrix}
x_{r,1}^p \\
x_{r,2}^p \\
x_{r,3}^p \\
x_{r,4}^p \\
\vdots \\
x_{r,m}^p
\end{bmatrix}
=
\begin{bmatrix}
r_1^p \\
r_2^p \\
r_3^p \\
r_4^p \\
\vdots \\
r_m^p
\end{bmatrix} & \label{eqn:primary-system-expanded} \\
\end{align}

\begin{align}
& \begin{bmatrix}
b_1^p & c_1^p \\
a_2^p & b_2^p & c_2^p \\
      & a_3^p & b_3^p & c_3^p \\
      &       & a_4^p & b_4^p & c_4^p \\
      &       &       &       &  \ddots & c_{m-1}^p\\
      &       &       &       &     a_{m}^p  & b_{m}^p
\end{bmatrix}
\begin{bmatrix}
u_1^p \\
u_2^p \\
u_3^p \\
u_4^p \\
\vdots \\
u_m^p
\end{bmatrix}
=
\begin{bmatrix}
-a_1^p \\
0 \\
0 \\
0 \\
\vdots \\
0
\end{bmatrix} & \label{eqn:secondary-system-1-expanded} \\
\end{align}
%
\begin{align}
& \begin{bmatrix}
b_1^p & c_1^p \\
a_2^p & b_2^p & c_2^p \\
      & a_3^p & b_3^p & c_3^p \\
      &       & a_4^p & b_4^p & c_4^p \\
      &       &       &       &  \ddots & c_{m-1}^p\\
      &       &       &       &     a_{m}^p  & b_{m}^p
\end{bmatrix}
\begin{bmatrix}
l_1^p \\
l_2^p \\
l_3^p \\
l_4^p \\
\vdots \\
l_m^p
\end{bmatrix}
=
\begin{bmatrix}
0 \\
0 \\
0 \\
0 \\
\vdots \\
-c_m^p
\end{bmatrix} & \label{eqn:secondary-system-2-expanded}
\end{align}
%
We refer to the subsystem in Eq. (\ref{eqn:primary-system-expanded})
the ``primary'' system, and the subsystems in
Eqs. (\ref{eqn:secondary-system-1-expanded}) and
(\ref{eqn:secondary-system-2-expanded})
the ``secondary'' systems.
Additionally, the following ``reduced'' system is solved:

@@

First, we note that
the secondary systems
[Eq. (\ref{eqn:secondary-system-1-expanded}) and
 Eq. (\ref{eqn:secondary-system-2-expanded})]
are dependent only on $\bm{a}$, $\bm{b}$ and $\bm{c}$,
the tridiagonal coefficients of the global tridiagonal system.
These are the same for all local grid lines,
so they are solved for a single local grid line in each subdomain.

>>>>

\usepackage{amsmath,bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{rotating}

@@

\hl{
Thus, cyclic reduction requires \emph{significantly} fewer steps
($2log_2(n) - 1$) compared to Thomas algorithm ($2n$).
Each step in cyclic reduction consists of operations on several indices
that can each be done in parallel,
making it a good fit for massively parallel architectures such as GPUs.}

@@

\begin{align}
& \begin{bmatrix}
b_1^p & c_1^p \\
a_2^p & b_2^p & c_2^p \\
      & a_3^p & b_3^p & c_3^p \\
      &       & a_4^p & b_4^p & c_4^p \\
      &       &       &       &  \ddots & c_{m-1}^p\\
      &       &       &       &     a_{m}^p  & b_{m}^p
\end{bmatrix}
\begin{bmatrix}
x_{r,1}^p \\
x_{r,2}^p \\
x_{r,3}^p \\
x_{r,4}^p \\
\vdots \\
x_{r,m}^p
\end{bmatrix}
=
\begin{bmatrix}
r_1^p \\
r_2^p \\
r_3^p \\
r_4^p \\
\vdots \\
r_m^p
\end{bmatrix} & \label{eqn:primary-system-expanded} 
\end{align}

\begin{align}
& \begin{bmatrix}
b_1^p & c_1^p \\
a_2^p & b_2^p & c_2^p \\
      & a_3^p & b_3^p & c_3^p \\
      &       & a_4^p & b_4^p & c_4^p \\
      &       &       &       &  \ddots & c_{m-1}^p\\
      &       &       &       &     a_{m}^p  & b_{m}^p
\end{bmatrix}
\begin{bmatrix}
u_1^p \\
u_2^p \\
u_3^p \\
u_4^p \\
\vdots \\
u_m^p
\end{bmatrix}
=
\begin{bmatrix}
-a_1^p \\
0 \\
0 \\
0 \\
\vdots \\
0
\end{bmatrix} & \label{eqn:secondary-system-1-expanded} 
\end{align}
%
\begin{align}
& \begin{bmatrix}
b_1^p & c_1^p \\
a_2^p & b_2^p & c_2^p \\
      & a_3^p & b_3^p & c_3^p \\
      &       & a_4^p & b_4^p & c_4^p \\
      &       &       &       &  \ddots & c_{m-1}^p\\
      &       &       &       &     a_{m}^p  & b_{m}^p
\end{bmatrix}
\begin{bmatrix}
l_1^p \\
l_2^p \\
l_3^p \\
l_4^p \\
\vdots \\
l_m^p
\end{bmatrix}
=
\begin{bmatrix}
0 \\
0 \\
0 \\
0 \\
\vdots \\
-c_m^p
\end{bmatrix} & \label{eqn:secondary-system-2-expanded}
\end{align}
%
We refer to the subsystem in Eq. (\ref{eqn:primary-system-expanded})
the ``primary'' system, and the subsystems in
Eqs. (\ref{eqn:secondary-system-1-expanded}) and
(\ref{eqn:secondary-system-2-expanded})
the ``secondary'' systems.
Additionally, the following ``reduced'' system is solved:

@@

First, we note that
the secondary systems
[Eq. (\ref{eqn:secondary-system-1-expanded}) and
 Eq. (\ref{eqn:secondary-system-2-expanded})]
are dependent only on $\bm{a}$, $\bm{b}$ and $\bm{c}$,
the tridiagonal coefficients of the global tridiagonal system.
\hl{These are the same for all local grid lines,
so they are \emph{precomputed} -
solved \emph{once} for a single local grid line in each subdomain.
This is done on the CPU.}
